Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2025-03-11 main.tex
described execution with and without recomputation. Minor edits in Section 6.C

@@

\subsection{Dynamic experiments on the memory-constrained cluster}
\label{sec.expe.dyn}

%\AB{Need to add results on the default cluster!}
%
%    \paragraph{Memory-constrained cluster}
The makespan in case of no recomputation\todo{TBD: clear?} becomes invalid as soon as at least one task finds itself in an invalid memory size
situation -- that is, if the scheduler assumed the task's memory to be smaller than actually needed and
assigned the task to a processor with not enough memory capacity.
Due to an extremely constrained memory in this cluster, only 134 experiments out of 1160 
for all algorithm variants \new{obtain a valid makespan when no recomputation is done}.

In the case of \heft, $14$ valid initial makespans were computed.
Out of them, $13$ remain valid until the end, after all the update requests,
\new{i.e., when accounting for the final execution time of each task and their memory requirement.}
The same $13$ experiments end with a valid makespan in case of no recomputation.
So, these workflows require so few resources that there is \new{nothing to be gained by re-scheduling them.}
%$13$ experiments ended with a valid makespan after recomputation in case of \heft, which corresponds to $4.4\%$ success
%rate. However, there were only $14$ successful \heft experiments overall in this setup, so for the successful experiments
%only, the success rate of not recomputing is $92\%$.

>>>>

\new{We call this execution mode execution \textit{with recomputation}.
Alternatively, the runtime system can execute \textit{without recomputation}.
It then follows the original schedule without sending the deviation values to the scheduler.

In this case, the runtime system waits for a blocked processor to become available if another task scheduled to it takes longer than expected.
If the predecessor task takes longer to execute, the runtime system leaves the processor of the current task
temporarily idle.
If any tasks take less time then expected, the runtime system ignores the opportunity to start other tasks earlier.
Finally, if there is not enough memory, the schedule is declared invalid and the execution stops.

The comparison to the makespan of the execution without recomputation shows how much improvement the exploration of dynamic
changes brings.
Moreover, the number of schedules that manage to stay valid despite the changes is an indicator of their robustness and the quality of the scheduler.
}

@@

\subsection{Dynamic experiments on the memory-constrained cluster}
\label{sec.expe.dyn}
\new{In this section, we compare the makespans of executions with and without recomputation.}
The makespan in case of no recomputation becomes invalid as soon as at least one task finds itself in an invalid memory size
situation -- that is, if the scheduler assumed the task's memory to be smaller than actually needed and
assigned the task to a processor with not enough memory capacity.
Due to an extremely constrained memory in this cluster, only 134 experiments out of 1160 
for all algorithm variants \new{obtain a valid makespan when no recomputation is done}.

In the case of \heft, $14$ valid initial makespans were computed.
Out of them, $13$ remain valid until the end, after all the update requests,
\new{i.e., when accounting for the final execution time of each task and their memory requirement.}
The same $13$ experiments end with a valid makespan in case of no recomputation.
So, these workflows require so few resources that
\new{the devations do not invalidate their scheduler. However, there is also nothing to be gained by re-scheduling them.}
%$13$ experiments ended with a valid makespan after recomputation in case of \heft, which corresponds to $4.4\%$ success
%rate. However, there were only $14$ successful \heft experiments overall in this setup, so for the successful experiments
%only, the success rate of not recomputing is $92\%$.
